\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}

### 2021-03-17 papers/intro_paper/results_lvc.tex
changes up to Sec. IV

For all the relevant signals, we show the posterior distributions
$(\df{220}, \dtau{220})$ in the left panel of
Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM
parameters, $(\fngr{220}, \taungr{220})$ in
Table~\ref{tab:qnm_o1o2_results}. In the right panel of
Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\%
credible intervals on the 1D marginalized posteriors. We highlight the
dependence of the constraints on the total mass of the
system. In general, the tightest bounds are set by the 
most massive systems, as they tend to have larger post-merger SNR. We
find a similar trend in the right panel of Fig.~\ref{fig:o1o2_events}.

>>>>

For all the relevant signals, we show the posterior distributions
$(\df{220}, \dtau{220})$ in the left panel of
Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM
parameters, $(\fngr{220}, \taungr{220})$ in
Table~\ref{tab:qnm_o1o2_results}. \comment{AB: could you explain how the mass 
and spin in Table II are computed? I think we should also list the mass and 
spin fron NR fits.} In the right panel of
Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\%
credible intervals on the 1D marginalized posteriors. We highlight the
dependence of the constraints on the total mass of the
system. In general, the tightest bounds are set by the 
most massive systems, as they tend to have larger post-merger SNR. We
find a similar trend in the right panel of Fig.~\ref{fig:o1o2_events}.
